% !TEX program = xelatex
\documentclass[]{resume-openfont}

\pagestyle{fancy}
\resetHeaderAndFooter

\setlength{\parindent}{1.5em}
\setlength{\parskip}{1.5em}
\renewcommand{\baselinestretch}{1.3}

%--------------------------------------------------------------
% Convenience command - make it easy to fill template

% Create job position command. Parameters: company, position, location, when
\newcommand{\resumeHeading}[4]{\runsubsection{#1}\descript{\\
#2}\hfill\location{#3 | #4}\fakeNewLine}

% Create education heading. Parameters: Name, degree, location, when
\newcommand{\educationHeading}[4]{\runsubsection{#1}\hspace*{\fill} \location{#3
 #4}\\
\textbf{#2}\fakeNewLine}

\newcommand{\teachingHeading}[4]{\runsubsection{#1}\hspace*{\fill} \location{#3
 #4} \textbf{#2}\fakeNewLine}

% Create project heading. Parameters: Name, link, Tech stack
\newcommand{\projectHeading}[3]{\Project{#1}{#2}
\descript{#3}\\}

\newcommand{\projectHeadingWithDate}[4]{\Project{#1}{#2}
\descript{#3 #4}\\}

% Parameters: courses
\newcommand{\courseWork}[1]{\textbf{Curso:} #1}

% Parameters: courses
\newcommand{\teacherAssistant}[1]{\textbf{Ayudante Alumno:} #1}
 
%--------------------------------------------------------------
\begin{document}

%--------------------------------------------------------------
%     Perfil
%--------------------------------------------------------------
\newcommand{\yourName}{Ocampo, Nicolás Benjamín}
\newcommand{\yourWebsite}{Blog}
\newcommand{\yourWebsiteLink}{https://benjaminocampo.netlify.app/}
\newcommand{\yourEmail}{nicolasbenjaminocampo@gmail.com}
\newcommand{\yourPhone}{~+54~(387)~15469~0467}
\newcommand{\githubUserName}{benjaminocampo}
\newcommand{\linkedInUserName}{benjamin-ocampo}

\begin{center}
    \Huge \scshape \latoRegular{\yourName}
\end{center}

%--------------------------------------------------------------
%     Datos Personales
%--------------------------------------------------------------

\noindent
\begin{minipage}{0.6\textwidth}

    \section{Personal Data}

    \sectionsep

    \large{\textbf{Name:} \yourName
    \vspace*{0.6em}

    \textbf{Birth's Place:} Salta Capital, Argentina
    \vspace*{0.6em}

    \textbf{Birth's Date:} July 15th, 1999
    \vspace*{0.6em}

    \textbf{Marital Status:} Single
    \vspace*{0.6em}

    \textbf{Phone Number:} \yourPhone
    \vspace*{0.6em}

    \textbf{E-mail:}
    \href{mailto:\yourEmail}{\underline{\yourEmail}}
    \vspace*{0.6em}

    \textbf{LinkedIn:}
    \href{https://www.linkedin.com/in/\linkedInUserName}{\underline{linkedIn/\linkedInUserName}}
    \vspace*{0.6em}

    \textbf{Website:} \href{\yourWebsiteLink}{\underline{\yourWebsiteLink}}
    \vspace*{0.6em}

    \textbf{GitHub:}
    \href{https://github.com/\githubUserName}{\underline{github/\githubUserName}}}
\end{minipage}
\hfill
\begin{minipage}{0.3\textwidth}\begin{flushright}
\end{flushright}
\end{minipage}%

%--------------------------------------------------------------
%     Educación
%--------------------------------------------------------------
\section{Education}

\educationHeading{Diplomatura en Ciencia de Datos, Aprendizaje Automático y sus
Aplicaciones}{Facultad de Matemática, Astronomía, Física, y Computación,
Universidad Nacional de Córdoba}{Córdoba, Argentina |}{Mar 2021 - Present}

\educationHeading{Licenciatura en Ciencias de la Computación}{Facultad de
Matemática, Astronomía, Física, y Computación, Universidad Nacional de Córdoba
\\
\faMortarBoard Overall mark: 9.58 over 10}{Córdoba, Argentina |}{Jan 2017,
Present}

This degree is considered equivalent to a Master in Computer Science degree. The
study plan has a duration of 5 years. This Master’s degree will also be obtained
by the end of 2021. Topic of the thesis: Using Word Embeddings for Heuristic
Grounding in Classical Planning.

\educationHeading{Analista en Computación}{Facultad de Matemática, Astronomía,
Física, y Computación, Universidad Nacional de Córdoba \\
    \faMortarBoard Overall mark: 9.56 over 10.}{Córdoba, Argentina |}{Jan 2017
- Dec 2019}

The study plan for this certification has a duration of 3 years.

\educationHeading{Escuela Secundaria}{Instituto de Educación Media Dr. Arturo
Oñativia \\
\faMortarBoard Overall mark: 9.22 over 10.}{Salta, Argentina}{Jan 2011 - Dec
2016}


%--------------------------------------------------------------
%     Courses Possibly Relevant to the Position
%--------------------------------------------------------------

\vspace*{0.5em}

\section{Courses I Have Done, Possibly Relevant to this Position}

\runsubsection{All the subjects I passed with mark 10 over 10 in the Facultad de
Matemática, Astronomía, Física, y Computación (FaMAF), Universidad Nacional de
Córdoba}

    \textbf{Discrete Mathematics II.} Graph algorithms. Maximum flow. Cyclic
    codes. P and NP problems.

    \textbf{Parallel Computing.} Program optimization techniques.
    
    \textbf{Neural Networks.} Dynamic systems. Modeling of real and artificial
    neurons.

    \textbf{Probability and Statistics.} Data analysis and visualization. Random
    variables. Statistical hypothesis testing.

    \textbf{Models and Simulation.} Random numbers. Generation of random
    variables. simulation of stochastic processes.

    \textbf{Mathematical Analysis I.} Continuous functions. Extreme values of
    continuous functions in closed intervals. Derivatives. Relative extremes.
    L'Hopital's rule. Successive derivatives. Applications to sketch functions.
    Notions of antiderivatives.

    \textbf{Mathematical Analysis II.} Integration methods, Successions and
    subsucessions. Numerical series. Power series. Taylor Series and
    polynomials. Analytical Geometry: lines and planes in $ R ^ n $. Functions
    of several real variables, partial derivatives, directional derivatives,
    gradient. Multiple integrals.

    \textbf{Numerical Analysis.} Error analysis: absolute and relative error;
    rounding and truncation; floating point systems. Solution of nonlinear
    equations: bisection, Newton, secant and fixed point methods. Polynomial
    interpolation and splines. Minimum squares. Numerical integration. Systems
    of linear equations.

    \textbf{Algorithms and Data Structures II.} Representation of data in
    memory. Data structures. Abstract types of data. Implementation of abstract
    data types. Pointers. Greedy algorithms. Divide and conquer. Multiple
    recursion and backtracking. Dynamic programming. Algorithmic complexity.

\runsubsection{Elective courses I participated in the RIO 2020 Summer School
located at Facultad de Ciencias Exactas, Físico-Químicas, y Naturales (FCEFyN),
Universidad Nacional de Río Cuarto, Argentina}

    \textbf{Classic and Neural Approaches to Text Mining.}
    Theoretical-practical analysis of unstructured information received in text
    format that arises from the interaction of Natural Language Processing,
    Information Retrieval and Machine Learning.

    \textbf{Software Testing.}
    Techniques and concepts of program verification such as fuzzing, symbolic
    execution, bounded model checking, among others.

\runsubsection{Teaching course I participated in the Diplomatura Aprender a
Enseñar dictated at the Universidad Nacional de Córdoba}

    \textbf{Diplomatura Aprender a enseñar.} Training for teaching assistants,
    and tutors to learn how to carry out their roles effectively at university.

\section{Participation in Seminars}

\educationHeading{Segmentation of Medical Images Using Neural
Networks}{Organized by the Grupo de Grandes Redes Sociales y Semánticas.
Duration: 1,30hs.}{}{FaMAF}

\educationHeading{Artificial Intelligence in Encrypted Data}{Organized by the
Grupo de Grandes Redes Sociales y Semánticas. Duration: 1,30hs.}{}{FaMAF}

\educationHeading{Integrating Interpretability and Efficiency in Early Risk
Detection in Social Networks}{Organized by the Grupo de Grandes Redes Sociales y
Semánticas. Duration: 1,30hs.}{}{FaMAF}

\educationHeading{Eye-tracking Applications in Visual and Mental
Health}{Organized by the Grupo de Grandes Redes Sociales y Semánticas. Duration
1,30hs.}{}{FaMAF}

\educationHeading{The Future of Mobile Development}{RIO 2020 Summer School,
Computer Science Department of the FCEFyN. Duration: 2hs.}{}{FCEFyN}

\educationHeading{Machine Learning — Solutions and Applications in Environment
Business}{Organized by the enterprise Futit Services in the RIO 2020 Summer
School, Computer Science Department of the FCEFyN. Duration: 2hs.}{}{FCEFyN}

\educationHeading{Business Intelligence — Reality and Experience}{Organized by
the enterprise Trimix in the RIO 2020 Summer School, Computer Science Department
of the FCEFyN. Duration: 2hs.}{}{FCEFyN}

\educationHeading{The Evolution of APIs: GraphQL}{Organized by the enterprise
WeDevelop in the RIO 2020 Summer School, Computer Science Department of the
FCEFyN. Duration: 2hs.}{}{FCEFyN}

%-------------------------------------------------------------
%     Experiencia Docente
%--------------------------------------------------------------

\section{Teaching Positions}
\teachingHeading{Teaching Assistant}{}{FaMAF |}{Mar 2020 - Present}

\textbf{Networks and Distributed Systems.} Preparation of extra material that
helps students in their study program. Schedule online meetings with groups of
students to answer any possible doubts.

\textbf{Operative Systems.} Preparation of extra material that helps students in
their study program. Schedule online meetings with groups of students to answer
any possible doubts.

\textbf{Algorithms and Data Structures I.} Solutions to didactic and cognitive
obstacles that affect student's progression. Assistance with marking and
correcting work.

\textbf{Programming Paradigms.} Schedule online meetings with groups of students
to answer any possible doubts.

\textbf{Introductory Course to Enter University.} Preparation of online lessons
under a stipulated schedule. Online support through chat applications.

\teachingHeading{Tutor}{}{FaMAF |}{Sep 2020 - Jun 2021}

Preparation of online tutorials for new students to introduce them to university
life. Organization of events to provide language coaching through conversation,
games, and activities.

\teachingHeading{Teaching Assistant}{}{Instituto Técnico Superior Córdoba,
Argentina |}{Sep 2020 - May 2021}

\textbf{Software Verification.} Help students to prepare for oral examinations
and practice their presentation skills.

%--------------------------------------------------------------
%     Proyectos de Inteligencia Artificial y Programación
%--------------------------------------------------------------
\section{Programming Projects (Artificial Intelligence and others)}

\projectHeading{Categorizing Announcements of the Enterprise Mercado
Libre}{https://github.com/benjaminocampo/Mentoria}{} \textbf{Developed in the
Diplomatura en Ciencia de Datos, Aprendizaje Automático y sus Aplicaciones,
FaMAF.} \\
\textbf{Programming languages and tools used in the project: Python, Keras,
Pandas, Scikit-learn, and NLTK.} \\
\textbf{Duration: 7 months (Ongoing).}

Development of a classifier to predict the correct category given the title of
an announcement from a dataset provided by the enterprise Mercado Libre for the
MeLi Challenge 2019.

\projectHeading{Navier Stokes Solver
Optimizations}{https://gitfront.io/r/user-1529562/1df7f0690a8d6eeffcb1cffeb1c3a408084afd08/navierstokes-mirror/}{}
\textbf{Developed in the Parallel Computing Course of the Licenciatura en
Ciencias de la Computación, FaMAF.} \\
\textbf{Programming languages and tools used in the project: C, C++, Python,
CUDA, Intrinsics, and ISPC.} \\
\textbf{Duration: 6 months.}

Application of a fluid dynamic simulation using numerical methods.
Implementation of low-level techniques that maximize its performance.
Development of Python scripts to pull, record, and produce output metrics.

\projectHeading{Personal Blog}{https://benjaminocampo.netlify.app/}{}
    \textbf{Extracurricular activity} \\
    \textbf{Programming languages and tools used in the project: ReactJS,
    GatsbyJS, and Javascript.} \\
    \textbf{Duration: 3 months.}

    Personal blog where I share my experiences, thoughts, and tutorials.

\projectHeading{Price Estimation of Properties in
    Melbourne}{https://github.com/benjaminocampo/DataCuration}{}
    \textbf{Developed in the Data Visualization Course of the Diplomatura en
    Ciencia de Datos, Aprendizaje Automático y sus Aplicaciones, FaMAF.} \\
    \textbf{Programming languages and tools used in the project: Python, and
    Pandas.} \\
    \textbf{Duration: 2 months.}

    Exploration and data curation of a dataset given by a Kaggle competition
    related to properties that were sold in Melbourne, Australia, between 2016
    and 2017. Preparation of a well-structured matrix in order to use supervised
    learning models to estimate their prices.

\projectHeading{Predictive and Generative Models for Neural
    Networks}{https://github.com/benjaminocampo/NeuralNetworks}{}
    \textbf{Developed in the Neural Networks Course of the Licenciatura en
    Ciencias de la Computación, FaMAF.} \\
    \textbf{Programming languages and tools used in the project: Python, and
    Pytorch.} \\
    \textbf{Duration: 2 months.}

    Analysis of the Lotka Volterra model that predicts a predator-prey
    environment and how two species interact. Implementation of the Integrate
    and Fire equations that models neural electric pulses to transmit
    information. Development and analysis of variational autoencoders which are
    neural networks for processing and generating images through an input sample
    and a defined model.


\projectHeading{Simulation of an ATM Queuing
System}{https://github.com/benjaminocampo/atm_simulator}{} \textbf{Developed in
the Models and Simulation Course of the Licenciatura en Ciencias de la
Computación, FaMAF.} \\
    \textbf{Programming languages and tools used in the project: Python.} \\
    \textbf{Duration: 1 month.}

    Implementation of a stochastic simulation of discrete events for arrival of
    customers to an ATM queuing system. Recording and plotting of simulation
    results.


%--------------------------------------------------------------
%     Experiencia en Investigación
%--------------------------------------------------------------
\section{Research Experience}

\teachingHeading{Using Word Embeddings for Heuristic Grounding in Classical
Planning}{}{FaMAF |}{Jul 2021 - Present}

    \textbf{Supervisors: Dr. M. Dominguez y Dr. C. Areces, FaMAF}

    Use of unsupervised and supervised techniques in AI Planning algorithms in
    order to improve their overall performance using fast machine learning
    models such as Logistic Regression, XGBoost, and Support Vector Machines.

%--------------------------------------------------------------
%     Actividades de Extensión
%--------------------------------------------------------------
\section{Community Service}

\teachingHeading{Technological Assistance to Vulnerable Sectors}{}{FaMAF}{Apr
2021 - Present}
    
    Reconditioning and installation of necessary software on computers, laptops,
    and tablets, so they could be donated to children, youth, and adults with
    difficulties in accessing technological resources.

%--------------------------------------------------------------
%     Actividades Extracurriculares
%--------------------------------------------------------------
\section{Extracurricular Activities}

\teachingHeading{RIO 2020 Summer Camp}{}{FCEFyN |}{Feb 2020}

Summer camp located at Universidad Nacional de Río Cuarto to participate in
Computer Science courses, seminars, and extracurricular activities.

\teachingHeading{Argentinian Programming Contest}{}{ACM International Collegiate
Programming Contest |}{Sep 2019}

Competition in groups of three members where I represented the FaMAF to solve a
set of algorithmic problems in the shortest possible time.

\vspace*{0.6em}
\teachingHeading{Training Camp Argentina}{}{FaMAF |}{Jul 2019}

Training to develop problem-solving skills in programming competitions.

\teachingHeading{Science Camp: Expedición Ciencia}{}{Neuquén, Argentina |}{Feb
2016}

Vocational camp in order to get a first approach to exploration and scientific
thinking.

\educationHeading{Music Composition Course: Trayecto Artístico
Profesional}{Escuela Superior de Música de la Provincia de Salta Nº 6003 José Lo
Giúdice}{Salta, Argentina |}{Mar 2012 - Dec 2014}
%--------------------------------------------------------------
%     Other Skills
%--------------------------------------------------------------
\section{Other Skills}

\paragraph{Languages:}
{\begin{minipage}{10cm}
    \begin{tabular}{|l||c|c|c|} \hline
                 &  {Reads}    &  {Speaks}   &  {Writes} \\ \hline \hline
    Spanish (Mother tongue) &  Very Well &  Very Well & Very Well \\
    English      & Very Well   & Well   & Well  \\ \hline
    \end{tabular}
    \end{minipage}} \\
\paragraph{Programming:}{Python, Scala, C, C++, Javacript, Java, Haskell.} \\
\paragraph{Technologies:}{Git, Pandas, NLTK, Sklearn, Pytorch, Keras, SQL,
MongoDB, \LaTeX, CUDA, Intrinsics, OpenMP, ISPC, ReactJS, GatsbyJS.} \\
\paragraph{Hobbies:}{Yoga, weightlifting, salsa and bachata dancing classes,
guitar player.}

\sectionsep
\end{document}